Quality Definitions of Qualities

### 2019-12-03 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated reliability

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=blue,       % color of links to bibliography
    filecolor=magenta,   % color of file links
    urlcolor=cyan           % color of external links
}

@@

\begin{defn}
  Installability is related to the amount of human effort required to install a
  software in a designated environment \citep{berander2005software}.
\end{defn}

\begin{defn}
  ``The capability of a software product to be installed in a specified
  environment'' \citep{berander2005software}.  \wss{remove the quotation marks -
    we are assuming all definitions are directly quoted from the source.  Please
  remove quotes for all of the definitions that you ``own.''}

@@

\begin{defn}
  A set of attributes that relate to the capability of software to maintain its
  level of performance under stated conditions for a stated period of time
  \citep{berander2005software}.
\end{defn}

\begin{defn}
  ``The capability of the software product to maintain a specified level of
  performance when used under specified conditions''
  \citep{international2001iso}.
\end{defn}

\begin{defn}
  Code possesses the characteristic reliability to the extent that it can be
  expected to perform its intended functions satisfactorily
  \citep{boehm2007software}.
\end{defn}

\begin{defn}
  A concern encompassing correctness and robustness \citep{meyer1988object}.
\end{defn}

\begin{defn}
  ``The extent to which a program can be expected to perform its intended
  function with required precision'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

\begin{defn}
``Informally, software is reliable if the user can depend on it''
\citep{ghezzi1991fundamentals}.
\end{defn}

Reliability is a critical quality for scientific software, since the results of
computations are meaningless, if they are not dependable.  Reliability is
closely tied to verifiability, since the key quality to verify is reliability,
while the act of verification itself improves reliability.

@@

\item Verification - Are we building the product right?  Are we implementing the
  requirements correctly (internal)
\item Validation - Are we building the right product? Are we getting the right
  requirements (external)
\item According to
  \href{https://en.wikipedia.org/wiki/Software_verification_and_validation}{Capability
    Maturity Model (CMM)}
\begin{itemize}
\item 
    Software Verification: The process of evaluating software to determine
    whether the products of a given development phase satisfy the conditions
    imposed at the start of that phase. [IEEE-STD-610] \wss{Need a proper citation}
  \item Software Validation: The process of evaluating software during or at the
    end of the development process to determine whether it satisfies specified
    requirements. [IEEE-STD-610] \wss{Need a proper citation}
\end{itemize}
\end{itemize}

>>>>

\usepackage{hyperref}
\hypersetup{
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=red,          % color of internal links (change box color with
%linkbordercolor)
citecolor=blue,       % color of links to bibliography
filecolor=magenta,   % color of file links
urlcolor=cyan           % color of external links
}

@@

\begin{defn}
	Installability is related to the amount of human effort required to install a
	software in a designated environment \citep{iso2001iec}
		{ berander2005software}.
\end{defn}

\begin{defn}
	The capability of a software product to be installed in a specified
	environment \citep{berander2005software}.  \wss{remove the quotation marks -
		we are assuming all definitions are directly quoted from the source.  Please
		remove quotes for all of the definitions that you ``own.''} 
\end{defn}

@@

\begin{defn}
	A set of attributes that relate to the capability of software to maintain its
	level of performance under stated conditions for a stated period of time \citep{international2001iso}. (As summarized in \citep{berander2005software}.)
\end{defn}

\begin{defn} \label{reliabilitySelected1}
	Probability of failure-free operation of a computer program in a specified environment for a specified time \citep{musa1987software}. (As stated in \citep{pressman2005software}.)
\end{defn}

\begin{defn}
	Code possesses the characteristic reliability to the extent that it can be
	expected to perform its intended functions satisfactorily
	\citep{boehm1976quantitative}.
\end{defn}

\begin{defn} \label{reliabilitySelected2}
   Reliability expresses the ability of the software to maintain a specified
   level of fault tolerance, when used under specified condition \citep{singh2013different}.
\end{defn}
\begin{defn}
	The extent to which a program can be expected to perform its intended
	function with required precision \citep{McCallEtAl1977}. (As summarized in
    \citet{VanVliet2000}.)
\end{defn}

\noindent \textbf{Proposed Definition}
Definition \ref{reliabilitySelected1} and \ref{reliabilitySelected2} rephrased : 	Probability of failure-free operation of a computer program in a specified environment for a specified time at a specified level of fault tolerance.

\wss{Needs to be completed.}\oo{Done}

\noindent \textbf{Reasoning}
Reliability is defined in a way that the measurement metrics are visible - the specified enviroment, the specified time and the specified level of fault tolerance. Reliability is a critical quality for scientific software, since the results of
computations are meaningless, if they are not dependable.  Reliability is
closely tied to verifiability, since the key quality to verify is reliability,
while the act of verification itself improves reliability.

@@

	\item Verification - Are we building the product right?  Are we implementing the
	requirements correctly (internal)
	\item Validation - Are we building the right product? Are we getting the right
	requirements (external)
	\item According to

	\href{https://en.wikipedia.org/wiki/Software_verification_and_validation}{Capability
		Maturity Model (CMM)}
	\begin{itemize}
		\item 
		Software Verification: The process of evaluating software to determine
		whether the products of a given development phase satisfy the conditions
		imposed at the start of that phase. [IEEE-STD-610] \wss{Need a proper
			citation}
		\item Software Validation: The process of evaluating software during or at the
		end of the development process to determine whether it satisfies specified
		requirements. [IEEE-STD-610] \wss{Need a proper citation}
	\end{itemize}
\end{itemize}
